A Plot is Worth a Thousand Tests: Assessing Residual Diagnostics with the Lineup Protocol

### 2023-10-25 paper.tex
reknit the pdf file

>>>>

{\centering \includegraphics[width=1\linewidth]{paper_files/figure-latex/nonlinearheterpower-1}

\caption{Comparison of power between different tests for (A) non-linear and (B) heteroskedasticity patterns (uniform fitted values only). Main plot shows the power curves, with dots indicating non-reject and reject in visual testing of lineups. The multiple lines for the visual test arise from estimating the power on many bootstrap samples. The row of scatterplots at the bottom are examples of residual plots corresponding to the specific effect sizes marked by vertical lines in the main plot.}\label{fig:nonlinearheterpower}
\end{figure}
